---
title: "Presentation Ninja"
subtitle: ""
author: "Tuyen mfe"
institute: ""
date: "2019/11/20"
output:
  xaringan::moon_reader:
    css: ["default", "style.css"]
    lib_dir: libs
    nature:
      highlightStyle: zenburn
      highlightLines: true
      countIncrementalSlides: false
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

???

Ảnh nền

---
class: inverse, center, middle

# Footnote

---

background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
background-size: cover;
class: center, bottom, inverse

# You only live once!

---

# Footnote

Để trình bày Footnote<sup>1</sup> chúng ta sử dụng cú pháp:

```{}
Text<sup>number_footnote</sup>

...
content
...

.footnote[
[1] Đây là Footnote 1
[2] Đây là Footenote 2
]
```

.footnote[
[1] Đây là Footnote 1
]

---

# Trình bày list

- one item
- one item
- one item
  - one more item
  - one more item
  - one more item

Code:

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```
---

# Nội dung xuất hiện từ từ

- Tôi là ai mà yêu đời quá vậy.

--

- Tôi là ai mà lòng còn nghi ngại. Khi đớn đau đang cào cấu quanh mình.

--

- Tôi là ai mà trước ánh bình minh. Lòng cứ muốn tan đi trong sắc nắng.

--

- Tôi là ai uống giọt đời cay đắng, không phải men nồng nào cũng ngát hương. 

--

Định dạng:

.left[One item]
.center[One item]
.right[One item]

---

class: inverse, center, middle

# Hai cột

---

# Ví dụ về hai column

.pull-left[
1. One item
2. One item
3. One item
]

.pull-right[
- One item
- One item
- Ome item
]

---

# Math expression

You can write LaTeX math expressions inside a pair of dollar signs, e.g. `$\alpha+\beta$` renders $\alpha+\beta$. You can use the display style with double dollar signs:

```{}
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

---

# R Code

```{r}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
```

---

# Table

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---

# Highlight Lines

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or have trailing comments `#<<`;

```yaml
output:
  xaringan::moon_reader:
    nature:
      highlightLines: true
```

Example:

```{r eval=FALSE, tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---

```{r, highlight.output=c(1, 3), echo=FALSE}
head(iris)
```

---
class: center, middle

# Thanks!